Challenges to transboundary fisheries management in North America under climate change

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Updated figures for thesis

@@

Fig5 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
grid.raster(Fig5)

@@

## DISCUSSION

@@

## CONCLUSIONS

@@

## LITERATURE CITED

@@

```{r FigureS11, eval = T, echo = F, fig.cap = "Outliers GoMA"}

>>>>

Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
grid.raster(Fig5)

@@

Fig5 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
grid.raster(Fig6)

@@

## Discussion

@@

## Conclusions

@@

## References

@@

```{r FigureS11, eval = F, echo = F, fig.cap = "Outliers GoMA"}
